Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-27 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
\textcolor{red}{The use of the power generation with a renewable energy source is growing rapidly due to the industrial development. Renewable energy is environment-friendly: clean, operates silently, long-lasting, low maintenance costs, zero fuel costs and an inexhaustible supply. Particularly, photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation.} The use of formal methods in electrical systems is a new subject with significant research spanning only the last five years. However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems. We propose a variant of the counterexample guided inductive synthesis approach with two phases linking the technical and cost analysis. First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time, which is validated via deployed systems in a riverside community in the Amazonas State (Brazil). We also present a comparison with a specialized simulation tool over real PV systems to show the effectiveness of our approach.
%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}

@@

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. \textcolor{red}{Generic optimization tools can be used as well, since that a PV system can be modeled as a non-linear set of equations. However, the industry demands that the presented solution be the optimum considering manufacturers, models and brands available on the market and not just minimum or maximum powers and values for the optimized items, and this is only possible with the use of specialist electrical systems optimization software.}

@@

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; \textcolor{red}{if the verification step dos not produces a FAIL result (i.e is unsatisfiable), the lower bound is adjusted; if it produces a FAIL, i.e is satisfiable, then a counterexample is provided with an optimal sizing.} % that meets both power reliability and system cost.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated symbolic verification in PV systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically, their use in synthesizing PV sizing is novel. Second, we evaluate our approach using different state-of-the-art symbolic verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER. Lastly, we discuss the main challenges of applying formal methods to PV systems and also reflect on lessons learned from this practical experience.

@@

Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using symbolic model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
 \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
 \STATE Initialize variables \\
 \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
 \STATE Declare the maximum possible cost $MaxCost$ \\
 \STATE Declare power demand, power peak, energy consumption \\
 \STATE Declare battery autonomy, depth of discharge, AC voltage \\
 \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost \\
	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
 \ENDFOR
 \RETURN $(\,)$ 
 \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%
Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2). We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5. The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, \textcolor{red}{which will be reached only if the optimal solution is not found first. If this $MaxCost$ was reached then there is not feasible solution to the problem.}

>>>>

\begin{abstract}
The use of power generation with a renewable energy source is proliferating due to industrial development. Photovoltaic (PV) panels have emerged as an alternative to fossil or nuclear fuel generation. The use of formal methods for PV systems is a new subject with significant research spanning only the last five years. 
%However, the use of automated synthesis to obtain optimal sizing of solar photovoltaic systems remains unexplored in literature. 
Here we develop and evaluate a sound, automated synthesis approach to obtain optimal sizing of stand-alone PV systems. We propose a variant of the counterexample guided inductive synthesis approach with two phases linking the technical and cost analysis. First, we synthesize a feasible candidate based on power reliability, which may not attain the lowest cost. Second, the candidate is then verified iteratively with a lower bound cost via model checking. If the verification step succeeds, the lower bound is adjusted; if it fails, a counterexample provides the optimal solution. Experimental results demonstrate that we can produce an optimal solution within an acceptable run-time. We also compare our formal approach with a commercial simulation tool over real PV systems to show its effectiveness.
%\keywords{Automated verification  \and Model Checking \and Solar photovoltaic systems.}
\end{abstract}

@@

In order to evaluate a PV system, there exist various specialized tools, e.g., RETScreen~\cite{Pradhan} and HOMER~\cite{Swarnkar}; and even general-purpose tools, e.g., MATLAB/Simulink~\cite{Gow1999}. However, these tools are based on simulation; they have the drawback of an incomplete coverage since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. Non-linear optimization tools could be employed since a PV system is typically modelled as a non-linear set of equations. However, the industry demands the final solution to be the optimum, considering manufacturers, models, and brands available on the market and not just minimum or maximum powers and values for the optimized items, which can only be achieved with specialist PV optimization software.

@@

Here we developed a variant of the counterexample guided inductive synthesis (CEGIS)~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06} technique for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, on each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via model checking with a lower bound that serves as the minimum cost of reference. If the verification step does not produce a counterexample, then the lower bound is adjusted; otherwise, we have achieved an optimal PV sizing.

Our work makes three significant contributions to advance the state-of-the-art in PV optimal sizing. First, the use of automated verification in PV systems was uncommon in recent prior studies; we have shown that formal methods can detect various errors in PV systems designed by existing commercial tools~\cite{TrindadeCordeiro19}. Here the application of formal methods to synthesize PV sizing is novel, thereby leading to more accurate results than existing commercial tools. Second, we evaluate our approach using different state-of-the-art verifiers to obtain the best performance in our verification back-end for synthesizing optimal PV systems and compare that to HOMER. Lastly, we discuss the challenges of applying formal methods to PV systems and reflect on lessons learned from this experience.

@@

Algorithm~\ref{alg:verification-algorithm} describes our pseudo-code to synthesize stand-alone PV systems using model checking~\cite{DBLP:journals/corr/abs-1909-13139}.
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE weather data (temperature, solar irradiance), list of equipment (datasheet and price), design requirements (load curve, peak demand, output voltage, battery autonomy), design assumptions (battery state of charge, criteria and objectives for technical and cost analysis).
 \ENSURE FAIL with counter-example showing the optimal sizing; SUCCESS, stating that the project has no feasible solution considering the requirements and the list of equipment available.
 \STATE Initialize variables \\
 \STATE Declare list of PV panels, controllers, batteries, and inverters data and cost \\
 \STATE Declare the maximum possible cost $MaxCost$ \\
 \STATE Declare power demand, power peak, energy consumption \\
 \STATE Declare battery autonomy, depth of discharge, AC voltage \\
 \FOR {$HintCost=0$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, E_{p} $ \\
	\STATE Calculate $N_{TPmin}, \, N_{PSmin}, N_{PPmin} $ \\
 	\STATE Calculate $C_{bank}$ \\
	\STATE Calculate $N_{BS}min, \, N_{BP}min, \, N_{B}total$ \\
	\STATE Requirement enforced by \textbf{assume}$(V_{c})$ \\
 	\STATE Calculate $I_{sc,amb}$ \\
 	\STATE Calculate $I_{c,min}$ \\
 	\STATE Requirement enforced by \textbf{assume}$(I_{c} \wedge V_{in}DC \wedge V_{out}AC)$ \\
	\STATE Requirement enforced by \textbf{assume}$(Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost \\
	\STATE $F_{obj} \leftarrow N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
 \ENDFOR
 \RETURN $(\,)$ 
 \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}
%
Our synthesis algorithm will synthesize constant values; it starts with the input of manufacturers' data and prices of PV panels, batteries, charge controllers, and inverters (Line 2). We define user requirements, i.e., house requirements and design definitions, from Lines 4 and 5. The \textit{for}-loop started at Line 6 controls the lowest cost to the PV solution. In particular, it starts with cost $0$ and stops only when the algorithm finds a feasible solution in which the cost breaks the $assertion$ stated in Line 22; if that happens, then our algorithm has found an optimal solution, thereby stating that the {\sc Verify} phase reached a satisfiable condition (\textit{SAT}). The $MaxCost$ value at Line 6 is just a very high value put as a limit to the \textit{for}-loop, \textcolor{red}{which will be reached only if the optimal solution is not found first. If this $MaxCost$ was reached then there is not feasible solution to the problem.}
